\huge Tor's Usability for Censorship Circumvention

### 2016-04-06 pets2017-paper/pets2017-paper.tex
Typo.

  \affil[1]{University of Caifornia Berkeley, E-mail: lnl@cs.berkeley.edu}

  \affil[2]{University of Caifornia Berkeley, E-mail: fifield@eecs.berkeley.edu}

  \affil[3]{University of Caifornia Berkeley, E-mail: nmalkin@cs.berkeley.edu}

  \affil[4]{University of Caifornia Berkeley, E-mail: ganesh.v@berkeley.edu}

  \affil[5]{University of Caifornia Berkeley and International Computer Science Institute, E-mail: egelman@cs.berkeley.edu}

  \affil[6]{University of Caifornia Berkeley, E-mail: daw@cs.berkeley.edu}

>>>>

  \affil[1]{University of California Berkeley, E-mail: lnl@cs.berkeley.edu}

  \affil[2]{University of California Berkeley, E-mail: fifield@eecs.berkeley.edu}

  \affil[3]{University of California Berkeley, E-mail: nmalkin@cs.berkeley.edu}

  \affil[4]{University of California Berkeley, E-mail: ganesh.v@berkeley.edu}

  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: egelman@cs.berkeley.edu}

  \affil[6]{University of California Berkeley, E-mail: daw@cs.berkeley.edu}
